TODO

### 2015-04-13 ccs.tex
Lets start with a clean Acknowledgements section for CCS

\identifying{
\section*{Acknowledgements}
Thanks to Richard Clayton, the mobile security reading group and Anil Madhavapeddy for reading various drafts of this paper.
Thanks to David Robertson for helpful advice on statistical analysis.
Thanks to Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities in Android.
}

>>>>

\identifying{
\section*{Acknowledgements}
}
